Based on polling as of 27 October 2024, Harris expects to win on 49.2%, leads Trump by 2% in 2024 US election

### 2024-10-30 paper/paper.qmd
update with plot caption

```{r}
# Predictions for Harris
new_data_harris <- new_data_harris |>
  mutate(
    predicted_unweighted = predict(model_harris_unweighted, newdata = new_data_harris),
    predicted_weighted = predict(model_harris_weighted, newdata = new_data_harris)
  )

@@

# Plotting with the filtered data
ggplot(combined_predictions_filtered, aes(x = end_date, color = candidate)) +
  geom_smooth(aes(y = predicted_unweighted, linetype = "Unweighted"), 
              method = "loess", se = FALSE, size = 1) +  # Unweighted model with smoothing
  geom_smooth(aes(y = predicted_weighted, linetype = "Weighted"), 
              method = "loess", se = FALSE, size = 1) +  # Weighted model with smoothing
  labs(title = "Predicted Support for Kamala Harris and Donald Trump \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  scale_linetype_manual(name = "Linear Model Type", values = c("Unweighted" = "dashed", "Weighted" = "solid")) +
  theme_minimal() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| label: fig-support-predicted
#| fig-cap: Predicted Support Trends for Kamala Harris and Donald Trump using fitted model
# Predictions for Harris
new_data_harris <- new_data_harris |>
  mutate(
    predicted_unweighted = predict(model_harris_unweighted, newdata = new_data_harris),
    predicted_weighted = predict(model_harris_weighted, newdata = new_data_harris)
  )

@@

# Plotting with the filtered data
ggplot(combined_predictions_filtered, aes(x = end_date, color = candidate)) +
  geom_smooth(aes(y = predicted_unweighted, linetype = "Unweighted"), 
              method = "loess", se = FALSE, size = 1) +  # Unweighted model with smoothing
  geom_smooth(aes(y = predicted_weighted, linetype = "Weighted"), 
              method = "loess", se = FALSE, size = 1) +  # Weighted model with smoothing
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",caption = 
                   "Weights: recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight\nLinear Regression Model: candidate support percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  scale_linetype_manual(name = "Linear Model Type", values = c("Unweighted" = "dashed", "Weighted" = "solid")) +
  theme_minimal() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
